Finding Quality Issues in SKOS Vocabularies

### 2012-03-24 analysis.tex
added some more analysis results

\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbrev.}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings & \textbf{MeSH} & ? & 24626 & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2112 & 1686 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & \textbf{DBPedia} & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings & \textbf{LCSH} & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Middle Kingdom tombs of Ancient Egypt Thesaurus & \texttt{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics & \textbf{STW} & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System & \textbf{NAICS} & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
\hline
Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}

@@

\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags & 0 & 0 & 23950 & 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\

@@

Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\

@@

Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1132 & 0 & 0 && 0 & 0 & 0 & 5 \\

Valueless Associative Relations & 9438 & 0 & 495 &&&&&&&&&&&& \\

Solely Transitively Related Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\

Omitted Top Concepts & 9 & 9 & 0 &&&&&&&&&&&& \\

Top Concept Having Broader Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\

@@

Missing In-Links &&&&&&&&&&&&&&& \\

Missing Out-Links &&&&&&&&&&&&&&& \\

Broken Links &&&&&&&&&&&&&&& \\

>>>>

\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbrev.}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings & \textbf{MeSH} & ? & 24626 & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2112 & 1686 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & \textbf{DBPedia} & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings & \textbf{LCSH} & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics & \textbf{STW} & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System & \textbf{NAICS} & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
\hline
Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}

@@

\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Issue} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags & 0 & 0 & 23950 & 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\

@@

Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & 743410 & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\

@@

Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1132 & 0 & 0 & 0 & 0 & 0 & 0 & 5 \\

Valueless Associative Relations & 9438 & 0 & 495 & 0 & 1 && 282 & 8120 & 0 & 0 & 1879 && 5082 & 0 & 5 \\

Solely Transitively Related Concepts & 0 & 0 & 0 & 0 & 2652 && 0 & 0 & 0 & 0 & 0 && 0 & 2189 & 0 \\

Omitted Top Concepts & 9 & 9 & 0 & 0 & 1 && 0 & 0 & 0 & 1 & 18 && 0 & 0 & 0 \\

Top Concept Having Broader Concepts & 0 & 0 & 0 & 1 & 0 && 0 & 0 & 0 & 0 & 0 && 0 & 0 & 0 \\

@@

Missing In-Links &&&&&&&&&&&&&&& 13411 \\

Missing Out-Links &&&&&&&&&&&&&&& 13411 \\

Broken Links & 0 & 0 & 1 & 99 &&& 238 & 0* & 11 & 7 && 425 & 1 & 3169 & n/a \\
